\subsection{Functional Requirements}
This phase covers the whole requirements for the system. After 
understanding the system we need the input data to the system then we 
watch the output and determine whether the output from the system is 
according to our requirements or not. So what we have to input and 
then what we’ll get as output is given in this phase.
\begin{itemize}
    \item{\bf Input Requirements of the System}
        \begin{enumerate}
            \item Students will enter feedback by answering a 
                questionare every week.
            \item At the end of questionare, students have to enter a 
                comment for teacher.
            \item Students can see previous comments about teacher and 
                they can give it a rating according to which it will be 
                appeared at teacher's dashboard as most rated comment.
            \item Teacher can give a message to students on overall 
                feedback which will be appeared on dashboard of every 
                student and HOD of department.
        \end{enumerate}
    \item{\bf Output Requirements of the System}
        \begin{enumerate}
            \item System will able to draw a performance graph of a
                teacher on weekly bases.
            \item Graphs will be appeared on HOD's and Teacher's dashboard.
            \item Teachers will able to see only thier own graph but HODs
                can select teacher and see thier performance graph.
            \item On basis of average rating and comments, favorite 
                teacher of the week will be selected and it will appeared
                on dashboard of every student, teacher and HODs.
        \end{enumerate}
\end{itemize}
\subsection{Software Requirements}
\begin{enumerate} 
    \item Programming language: Python 2.7+
    \item Framework: Django 1.5
    \item Web Languages: Html, Java Script, CSS 
    \item Database: MySQL Database Server 5.1 
    \item Documentation: Doxygen 1.8.3
    \item Text Editor: Gedit, Vim
    \item Operating System: Ubuntu 12.04 +
    \item Debugger: Django Debugger, Django shell, Terminal
    \item Web Server: Apache 2.4
\end{enumerate}
\subsection{Performance Requirements}
\begin{enumerate}
    \item System must be reliable and fast so that there is no delay in
        desplaying result.
    \item Errors should be handeled smoothely.
\end{enumerate}
